Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic: adapted to CHOP input format

### 2022-01-25 metanalysis_visualization/results_all_sites.Rmd
fix the colnames of the CHOP outputs to match with the rest of sites. create a markdown to visualize the current outputs together

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(i)
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    bootstrapped_fitted_all <- bootstrapped_fitted_df
    bootstrapped_coefficients_all <- bootstrapped_coefficients_df
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
  } else {
    count_icd_all <- rbind(count_icd_all, count_icd)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    bootstrapped_fitted_all <- rbind(bootstrapped_fitted_all, bootstrapped_fitted_df)
    bootstrapped_coefficients_all <- rbind(bootstrapped_coefficients_all, bootstrapped_coefficients_df)
   mental_codes_qc_output <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all, mental_codes_qc_output)
  }
  rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
     perc_disorder_group,ratios_patients_with_without_psy,
     patient_count_psy_period_psy_clear, table1, bootstrapped_coefficients_df,
     bootstrapped_fitted_df, mental_codes_qc_output)
}
```

## Percentage: patients with psychiatric conditions / total number of patients

@@

```{r}
### add CHOP 
ratios_patients_with_without_psy_chop <- read.delim ( file = "/Users/alba/Desktop/ratios_patients_with_without_psy_chop.txt")

ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy_chop)

ratios_patients_with_without_psy_all %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=percentage, 
              group = siteid, color = siteid))+
  geom_point( aes(shape=siteid, color=siteid) )+
    geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Percentage: patients with psychiatric conditions / total number of patients") +
    xlab("period (months)")
```

@@

### Summary of the codes used per site 
```{r, eval=FALSE}
mental_codes_qc_output_all <- mental_codes_qc_output_all %>%
    mutate( concept_code = gsub("[.]", "", concept_code ) ) %>%
  unique()

summary_codes <- mental_codes_qc_output_all %>%
  select( disorder_group, description, concept_code, distinct_patients, siteid ) %>%
  spread( siteid, distinct_patients)

## add a column with the sites combination 
getSitesWithEachCode <- function(row) {
  sites <- c( row['BCH'],  row['Lurie'], row['UMICH'], row['FRBDX'], row['APHP'])
  sites <- sites[!is.na( sites ) ]
  siteVal <- paste0( names( sites ), collapse = " - ")
  return( siteVal)
}
summary_codes <- summary_codes[, c("disorder_group", "description", "concept_code", 
                                   "BCH", "Lurie", "UMICH",  "FRBDX", "APHP") ]                        
summary_codes$sitesCombination <- apply(summary_codes, 1, FUN = getSitesWithEachCode)
summary_codes <- summary_codes[
  with(summary_codes, order(BCH, FRBDX, Lurie, UMICH, APHP, decreasing = TRUE)),
]
print( paste0("There are in total ", nrow( summary_codes[ summary_codes$sitesCombination == "BCH - Lurie - UMICH - FRBDX - APHP", ]), " codes in common across all sites"))

write.table( summary_codes, file="summary_codes.txt", col.names = TRUE, row.names = FALSE, sep = "\t", quote = FALSE )

#### upSetR 
upsetForDisorderGroup <- function( df, disorderGroup = "ALL"){
  if( disorderGroup != "ALL"){
     df <- df %>%
       filter( disorder_group == disorderGroup ) 
  }

  BCH_concepts = df[ df$siteid == "BCH", "concept_code"]
  FRBDX_concepts = df[ df$siteid == "FRBDX", "concept_code"]
  Lurie_concepts = df[ df$siteid == "Lurie", "concept_code"]
  UMICH_concepts = df[ df$siteid == "UMICH", "concept_code"]
  APHP_concepts = df[ df$siteid == "APHP", "concept_code"]

  concepts = list( 
          BCH = BCH_concepts$concept_code,
          FRBDX = FRBDX_concepts$concept_code, 
          Lurie = Lurie_concepts$concept_code, 
          UMICH = UMICH_concepts$concept_code, 
          APHP  = APHP_concepts$concept_code
          )
  output <- upset(fromList(concepts), order.by = "freq")
  return( output )
}

upsetForDisorderGroup( df = mental_codes_qc_output_all, disorderGroup = "ALL")
```

### Estimate number of ICD codes per site and disorder group
Represent this in 16 pannels, if we put all together, due to the different scales we will not be able to really see the differences between results. 
```{r, eval=FALSE}
numberOfCodesPerDisorderGroup <- mental_codes_qc_output_all %>%
  group_by( disorder_group, siteid ) %>%
  mutate( icd_codes_count = n( )) %>%
  select( disorder_group, siteid, icd_codes_count ) %>%
  unique()

swr = function(string, nwrap=30) {
  paste(strwrap(string, width=nwrap), collapse="\n")
}
swr = Vectorize(swr)

numberOfCodesPerDisorderGroup %>%
  mutate( disorder_group = swr( disorder_group ) ) %>%
  ggplot( aes( x= reorder( siteid, icd_codes_count), y = icd_codes_count)) +
  geom_bar( stat = "identity") +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
```

>>>>

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(outputFiles[i])
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    bootstrapped_fitted_all <- bootstrapped_fitted_df
    bootstrapped_coefficients_all <- bootstrapped_coefficients_df
  } else {
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc )
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    bootstrapped_fitted_all <- rbind(bootstrapped_fitted_all, bootstrapped_fitted_df)
    bootstrapped_coefficients_all <- rbind(bootstrapped_coefficients_all, bootstrapped_coefficients_df)
  }
  rm(patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
     perc_disorder_group,ratios_patients_with_without_psy,
     patient_count_psy_period_psy_clear, bootstrapped_coefficients_df,
     bootstrapped_fitted_df)
}
```

@@

```{r}
ratios_patients_with_without_psy_all %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=percentage, 
              group = siteid, color = siteid))+
  geom_point( aes(shape=siteid, color=siteid) )+
    geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Percentage: patients with psychiatric conditions / total number of patients") +
    xlab("period (months)")
```

@@

### 2022-01-25 psy_peds_3_CHOP.Rmd
fix the colnames of the CHOP outputs to match with the rest of sites. create a markdown to visualize the current outputs together

```{r}
# estimate the percentage using as denominator the total number of patients per month with any psychiatric condition
perc_disorder_group <- count_disorder_group %>%
  mutate( percentage_dg = 100*count_dg / count_psy_patients )

@@

```{r}
##percentage
patients_hospitalized_agg_sex_perc <- psyCounts %>%
  left_join( patients_hospitalized_agg_sex, by = c("time_p")) %>% 
  replace_na(list(count_sex = 0))
patients_hospitalized_agg_sex_perc$percentage <- 100*patients_hospitalized_agg_sex_perc$count_sex/patients_hospitalized_agg_sex_perc$count_psy_patients
patients_hospitalized_agg_sex_perc %>%
  ggplot(aes(x = time_p, y = percentage, fill = sex)) +
  geom_bar(stat="identity", position = "dodge")+
  scale_fill_manual(values = cbPalette) +
  labs(y = "Percentage ",
       x = time_period,
       title = paste0("Patient (%) per ", time_period," aggregated by sex"),
       subtitle = "Per Sex") + 
  theme(legend.position = "bottom") + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=sex), colour= "black", size = 0.5)
```

>>>>

```{r}
# estimate the percentage using as denominator the total number of patients per month with any psychiatric condition
perc_disorder_group <- count_disorder_group %>%
  mutate( percentage_dg = 100*count_dg / count_psy_patients ) %>%
  select( time_p, count_icd = count_psy_patients, period, disorder_group, count_dg, percentage_dg )

@@

```{r}
##percentage
patients_hospitalized_agg_sex_perc <- psyCounts %>%
  left_join( patients_hospitalized_agg_sex, by = c("time_p")) %>% 
  replace_na(list(count_sex = 0))
patients_hospitalized_agg_sex_perc$percentage <- 100*patients_hospitalized_agg_sex_perc$count_sex/patients_hospitalized_agg_sex_perc$count_psy_patients
patients_hospitalized_agg_sex_perc <- patients_hospitalized_agg_sex_perc %>% 
  select( time_p, count= count_psy_patients, sex, count_sex, percentage )
patients_hospitalized_agg_sex_perc %>%
  ggplot(aes(x = time_p, y = percentage, fill = sex)) +
  geom_bar(stat="identity", position = "dodge")+
  scale_fill_manual(values = cbPalette) +
  labs(y = "Percentage ",
       x = time_period,
       title = paste0("Patient (%) per ", time_period," aggregated by sex"),
       subtitle = "Per Sex") + 
  theme(legend.position = "bottom") + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=sex), colour= "black", size = 0.5)
```
